---
title: "Chapter 17 DC Exercises"
auhtor: "Kavond Jones"
output: html_notebook
---

## Assigned Exercises 
- Chapter 17: 17.1, 17.3, 17.4, 17.5, 17.7

```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(mosaic)
library(tidyverse)
library(dcData)
library(dplyr)
```

## 17.1 
- Boys' names ending in a vowel 
```{r}
Boys<-
  BabyNames%>%
  filter(sex != "F")%>%
  group_by(name)%>%
  summarise(total = sum(count))

Boys
```

```{r}
Boys%>%
  filter(grepl("[aeiou]$", name))%>%
  arrange(desc(total))%>%
  head(10)
```

- Names ending with "joe" 
```{r}
BabyNames%>%
  filter(grepl("joe$", name, ignore.case = FALSE))%>%
  group_by(name)%>%
  summarise(total = sum(count))%>%
  arrange(desc(total))%>%
  head(10)
```

## 17.3
- A type of string that would use this type of styling is a phone number. Additionally a postal code, zip code, or even social security number would be familiar to this general expression.

## 17. 4
1. The strings that match the pattern will be exactly 2 characters long. 
2. 61 different strings will match the. 
3. The pattern represents all the different combinations of two letters to represent the states and territories located in the "US".

## 17.5 
```{r}
BibleNames <- 
  readr::read_csv("https://mdbeckman.github.io/dcSupplement/data/BibleNames.csv")
```

1. Names that have "bar", "dam", or "lory" in them.
```{r}
BibleNames%>%
  filter(grepl("bar|dam|lory", name, ignore.case = TRUE))
```

2. Names that end with those words. 
```{r}
BibleNames%>%
  filter(grepl("bar$|dam$|lory$", name, ignore.case = FALSE))
```

## 17.7 - Data table showing total number of babies for each bible related name. Top 10 names
```{r}
BibleRelated<-
  BabyNames%>%
  inner_join(BibleNames)%>%
  group_by(name)%>%
  summarise(total = sum(count))%>%
  arrange(desc(total))%>%
  head(10)
```
```{r}
BibleRelated
```

