---
title: "Chapter 7"
author: "Kavond Jones"
output: html_notebook
---

## Assigned Exercises 
- Chapter 7: 7.1, 7.2, 7.3, 7.4, 7.5, 7.6, 7.8 

# Required Packages 
```{r}
rm(list = ls())
library(mosaicData)
library(mosaic)
library(tidyverse)
library(dcData)
```

# Chapter 7
## 7.1 - Transformation or reduction
1. Reduction
2. Neither 
3. Reduction 
4. Transformation
5. Transformation 
6. Reduction 
7. Transformation 
8. Reduction 

## 7.2 - Statements with Error 
a. Group baby names by "First" and summarise by the total votes each received. Error: There was no object assigned before calling the dataframe. 
b. Group the dataframe by year and sex and give a summary of the total births by years and sex. Error: the BabyNames dataframe was never called and was used in the argument for the group_by function. 
c. Group the names in BabyNames by year and sex and then sum of the births. Error: object 'BabyNames' not found 

## 7.3 - Minneapolis2013
1. 80101 Cases
```{r}
glimpse(dcData::Minneapolis2013)
```
2. 
```{r}
Minneapolis2013 %>%
  group_by(Second) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  head(5)
```
3. 
```{r}
Minneapolis2013 %>%
  group_by(First) %>%
  summarise(count = n()) %>%
  filter(First == "undervote")
```
```{r}
Minneapolis2013 %>%
  group_by(Second) %>%
  summarise(count = n()) %>%
  filter(Second == "undervote")
```
```{r}
Minneapolis2013 %>%
  group_by(Third) %>%
  summarise(count = n()) %>%
  filter(Third == "undervote")
```
4. 
```{r}
Minneapolis2013 %>%
  group_by(First, Second) %>%
  summarise( count= n()) %>%
  arrange(desc(count)) %>%
  head(3)
```
5. 
```{r}
Minneapolis2013 %>%
  group_by(Precinct) %>%
  summarise(count = n()) %>% 
  arrange(desc(count)) %>%
  head(1)
```
## 7.4 Statemanets with error 
a. 
```{r}
BabyNames %>%
  group_by(year, sex) %>%
  summarise(BabyNames, total=sum(count))
```

b. 
```{r}
ZipGeography %>%
  group_by(State) %>%
  summarise(pop = sum(Population))
```
c. 
```{r}
Minneapolis2013 %>%
  group_by(First) %>%
  summarise(voteReceived = n())
```

d. 
```{r}
Minneapolis2013 %>%
  group_by(First) %>%
  summarise(voteReceived = n())
```

## 7.5 
a. 
```{r}
VoterData_A <-
  Minneapolis2013 %>%
  group_by(First, Second)

View(VoterData_A)
```

```{r}
View(Minneapolis2013)
```
- There is no difference between the two data frames. 
b. 
```{r}
VoterData_B <-
  Minneapolis2013 %>%
  summarise( total = n() )

View(VoterData_B)
```
- Compared to Minneapolis2013 data, VoterData_B shows only the total number of cases. 

c. 
```{r}
VoterData_C <-
  Minneapolis2013 %>%
  group_by(First, Second) %>%
  summarise( total = n() )

View(VoterData_C)
```
- No different between first and second votes between this data frame and the Minneapolis2013. The only apparent tweak is tha this VoterData_C is in Alphabetical order. A case is the first and second vote with the total count of the combination of them.

d. R has no idea what to summarise the total of so it needs a column first.

## 7.6 
- 1
```{r}
data("ZipGeography")

LandPop <- 
  ZipGeography %>%
  select(State, Population, LandArea, ZIP) %>%
  group_by(State) %>% 
  summarise(POPSUM = sum(Population, na.rm = TRUE), 
            LandSUM = sum(LandArea, na.rm = TRUE),
            POPperLandSUM = sum(Population, na.rm = TRUE)/sum(LandArea, na.rm = TRUE))
```

```{r}
ggplot(data = LandPop,
       aes(x = LandSUM, 
           y = POPSUM)) + 
  geom_point() + 
  aes(colour = State)
```

- 2
```{r}
LandPop %>%
  mUSMap(key = "State", fill = "POPSUM")
```

- 3
```{r}
LandPop %>%
  mUSMap(key = "State", fill = "POPperLandSUM")
```

## 7.7 
a. Sex, Count, meanAge 
b. Diagnosis, count, meanAge 
c. sex, diagnosis, count, meanAge 
d. age, diagnosis, count, meanAge 
e. age, count, meanAge

## 7.8 
1. 
```{r}
data("ZipDemography")

ggplot(ZipDemography, aes(x=Foreignborn, y=SpeakalanguageotherthanEnglishathome5yearsandover)) + geom_point()
```
2. Sort the data frame by the foreigners Zipcodes and then by state, and then calculate the Bachelorsdegreeorhigher by getting the total sum(count) of each state. 

