---
title: "Chapters 5&6"
author: "Kavond Jones"
output: html_notebook
---

## Assigned Exercises 
- Chapter 5: 5.1, 5.2, 5.3 
- Chapter 6: 6.1, 6.2, 6.3, 6.4, 6.5, 6.6, 6.7, 6.8, 6.9, 6.10

# Required Packages 
```{r}
rm(list = ls())
library(mosaicData)
library(mosaic)
library(tidyverse)
library(dcData)
```


# Chapter 5 
## 5.1 reconstruct the graph 
```{r}
mplot(CPS85)
```
```{r}
CPS85 %>%
  ggplot(aes(x = sex, y = wage, fill = married )) + 
  geom_bar(stat = 'identity', position = 'dodge', width = .9) + 
  facet_wrap(~race, ncol = 3)
```
## 5.2 - Remaking graph... 
```{r}
ggplot(data = NCHS, aes(x = bmi)) + 
  geom_density(adjust = 1, alpha = .4, color = NA)+
  aes( color = sex, fill = sex )+
  facet_wrap(~ pregnant, ncol = 4)+
  labs(title = "NCHS Data - Prenancy BMI - Male VS Female ")+
  theme(legend.position = "right")+
  theme_bw()
```
## 5.3 - Make this graphic of the CPS85 data 
```{r}
ggplot(data = CPS85, aes(x = exper, y = wage))+ 
  geom_point()+
  aes(colour = married)+
  facet_wrap(~ sector, ncol = 4)+
  scale_x_log10()+
  scale_x_log10()+
  theme_bw()
```


# Chapter 6 
## 6.1
1. "1433B", "1433E", "1433G", "1433Z"
2. Yes, axes remain constant in all facets. 
3. Asterisks, Red lines and black vertical lines.

## 6.2 
1. Y-Axis(Log Enzyme), X-Axis(genes), Fill(Flux), Color(molecule), target(sections of X-axis)
2. Location of the graph(Gene, Log Enzyme, Target), color(molecule), fill(flux)
3. Gene and Log Enzyme Concentration
4. Gene and the target . 

## 6.3 
1. (1) Vertical Line w/ dot(center, high and low stats of the protein). (2) Stars(protein signif.)
2. Horizontal(protein), Vertical(low/center/high stats)
3. Yes, based of the polarity of the proteins. 
4. Y-Axis with tick marks to judge the low/center/high of the proteins. Label "Apico-basal cell polarity proteins".

## 6.4
1. The frame is time and the trains departing at that time. 
2. Solid, dash, and dotted lines. 
3. Solid Lines(public transport), Dashed lines(transfers), dotted lines(walking). Position with time(time and route taken)
4. Time of day, type transportation, length(time) of transportation.

## 6.5 
a. Forecast Probability, State(y-axis) 
b. State(y-axis), Polling Organization(x-axis)
c. Blue for democrats, red for republicans 
d. State(y-axis)
e. Glyph colors 

## 6.6 
a. Rectangle w/ Words. Black font 
b. Rectangle color of logo and name of org.
c. Polling org's state forecast.
d. Polling org's forecast by state. Whiter the higher text means higher the likelihood.  

## 6.7 
a. The states with more dominant forecast are put at both ends while the toss ups lie in the middle.
b. The certainty of the poll and their projected forecast. 
c. Roth poll probability for the Demographic Candidate. 
d. NYT poll probability for the Demographic candidate. 
e. The polls placement. 

## 6.8
a. Vertical scale: Name of state. 
e. Color: color band.

## 6.9 
```{r}
Small <-
  NCHS %>%
  sample_n(size= 5000)
```

```{r}
Small %>%
  ggplot(aes(x = bmi, y = weight) +
  geom_point() +
  aes(colour = smoker) +
  theme_bw()
```


