---
title: "DC Exercises Chapter 15"
author: "Kavond Jones"
output: html_notebook
---

## Assigned Exercises 
- Chapter 15: 15.1, 15.2, 15.3, 15.4, 15.5

```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(mosaic)
library(tidyverse)
library(esquisse)
library(dcData)
library(dplyr)
```

## 15.1 
```{r}
CPS85 %>%
  ggplot(aes(x = sex, y = wage, fill = sex))+
  geom_boxplot()
```

## 15.2 
1. Judging from the graph, i would say the most likel;y height among the NCHS people is 1.65
2. Judging from the graph, i would estimate the womens most likely height to be around 1.6 and for men, 1.75.
3. Based on the the graph, the most likely BMI for a 40 year old to is 27. For a 70 year old, 27 as well. 

## 15.3 
```{r}
CPS85%>%
  ggplot(aes(x = educ, y = wage, color = sex))+
  stat_smooth(method = lm)+
  geom_point()
```

## 15.4 
```{r}
library(mosaicData)

Galton%>%
  ggplot(aes(x = height, y = mother))+
  geom_density_2d()+
  facet_wrap(~ sex)
```

## 15.5
1a. The data actually indicates the opposite. The more elderly, the less children are likely. 
2a. Seeing that the confidence band is relatively narrow, it doesn't seem that there's a consistency. 
1b. No, the representation of a flat line would not be consistent with the data. 
2b. The ration is roughly 4 times smaller when comparing graphs. 
3b. The does seem right considering the band shrinks as it gets to the middle. 



