---
title: "DC Exercises Chapters 13 & 16"
author: "Kavond Jones"
output: html_notebook
---

## Assigned Exercises 
- Chapter 13: All 
- Chapter 16: 16.1, 16.2 

```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(mosaic)
library(tidyverse)
library(esquisse)
library(dcData)
library(dplyr)
```

# Chapter 13 
## Problem 13.1 

- Top 5 for males 
```{r}
BabyNames%>%
  filter(sex == "M")%>%
  group_by(name)%>%
  summarise(total = sum(count))%>%
  filter(rank(desc(total)) <= 5)
```

- Top for Females 
```{r}
BabyNames%>%
  filter(sex == "F")%>%
  group_by(name)%>%
  summarise(total = sum(count))%>%
  filter(rank(desc(total)) <= 5)
```


## Problem 3.2 
### 1. 

```{r}
topHundred<-
  BabyNames%>%
  group_by(year)%>%
  filter(rank(desc(count)) <= 100)%>%
  summarise(total = sum(count))
```

```{r}
belowHundred<-
  BabyNames%>%
  group_by(year)%>%
  filter(rank(desc(count)) > 100)%>%
  summarise(total = sum(count))
```

```{r}
Mixed<-
  belowHundred%>%
  inner_join(topHundred, c("year" = "year"))%>%
  rename(Top_100 = total.y)%>%
  rename(Below = total.x)
```


```{r}
Mixed<-
  Mixed%>%
  pivot_longer(cols = c(Below, Top_100), names_to = "ranking", values_to = "total")%>%
  arrange(desc(year))
Mixed
```

### 2. 
```{r}
Fraction<-
  Mixed%>%
  pivot_wider(names_from = ranking, values_from = total)%>%
  mutate(fractop_100 = Top_100 / Below + Top_100)
```

### 3. 
```{r}
ggplot(Fraction) +
  aes(x = year, y = fractop_100)+
  geom_line()+
  labs(x = "Year", y = "Fraction of babies", title = "Change in baby names for top 100 each year")+
  theme_minimal()
```

## 13.3 
```{r}
Top50 <-
BabyNames%>%
  group_by(year)%>%
  filter(rank(desc(count)) <= 50)
```

```{r}
Unpopular <-
BabyNames%>%
  group_by(year)%>%
  filter(rank(desc(count)) > 1000)
```


# Chapter 16
```{r}
#Call lubridate package 
library(lubridate)
```

## 16.1 

### 1. "April 30, 1777" Johann Carl Friedrich Gauss
```{r}
#use mdy to convert the chr string into a date variable
Johann <- 
  mdy("April 30, 1777")
```

```{r}
#Setting my birthday
David <-
  mdy("March 10 2000")
```

```{r}
#The difference in days is by subtracting them 
David - Johann
```

### 2. "06-23-1912" Alan Turing’s birthday
```{r}
Alan<- 
  mdy("06-23-1912")

David - Alan
```

### 3. "3 March 1847" Alexander Graham Bell’s birthday
```{r}
Alexander<- 
  dmy("3 March 1847")

David - Alexander
```

### 4. "Nov. 11th, 1918 at 11:00 am" Armistice ending World War I on the Western Front.
```{r}
Armistice<- 
  mdy_hm("10-11-1918 11:00")
David<- 
  mdy_hm("03-10-2000 12:03")

David - Armistice
```

### 5. "July 20, 1969" First manned moon landing
```{r}
Moon<- 
  mdy("July 20, 1969")
David <- 
  mdy("March 10, 2000")

David - Moon
```

## Problem 16.2

1. readr::parse_number()

2. readr::parse_number() will turn it into 17 but not .17

3.Neither change nineteen into the actual number 19

4.readr::parse_number()

5.readr::parse_number() 

6.readr::parse_number()

7.neither will work 

8.both

9.readr::parse_number() converts it  

